Thermodynamic fragments in magic state theories

### 2020-07-13 magic_paper.tex
Minimum copies plot

All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) =$
\begin{equation}\label{eq:leftelb}
	\left( \frac{1}{9^n} \sum\limits_{j=0}^{k-1} 8^{2j} \binom{n}{2j}, \frac{1}{3^n} \sum\limits_{j=0}^{k-1} 4^{2j} \binom{n}{2j} \right)
\end{equation}
for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}^{\otimes n}}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
\begin{equation}\label{eq:rightelb}
	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k'-1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k'-1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
\end{equation}
for all elbows right of the maximum, $k' = k_\star, \dots, n$.

\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}). 
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

>>>>

All $n$ elbows, depicted in the diagram of~\cref{fig:lccalc}, are given by the following sums, $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) =$
\begin{equation}\label{eq:leftelb}
	\left( \frac{1}{9^n} \sum\limits_{j=0}^{k-1} 8^{2j} \binom{n}{2j}, \frac{1}{3^n} \sum\limits_{j=0}^{k-1} 4^{2j} \binom{n}{2j} \right)
\end{equation}
for all elbows left of the maximum, $k = 1, \dots, k_\star = \floor{\frac{n}{2}}+1$ and $\left( x_k, \lc{\ketbra{\rm{S}}^{\otimes n}}{\frac{1}{d}\id}(k) \right) = (x_{k_\star}, L(k_\star)) + $
\begin{equation}\label{eq:rightelb}
	\left( \left(\frac{8}{9}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 8^{-(2j+1)} \binom{n}{2j+1}, \left(\frac{4}{3}\right)^n \sum\limits_{j=0}^{k' - k_\star - 1} 4^{-(2j+1)} \binom{n}{2j+1} \right),
\end{equation}
for all elbows right of the maximum, $k' = k_\star + 1, \dots, n$.

\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$ (corresponds to red curve in~\cref{fig:stab_distill}); \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$ (corresponds to blue curve in~\cref{fig:stab_distill}). 
    }%
    \label{fig:lcs}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill_copies.pdf}
    \caption{\textbf{Copies required for Strange state distillation.} Mana and Lorenz curve copy thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
    Lorenz curve comparison consistently provides higher low bounds on the number of noisy Strange state copies required.
    }
    \label{fig:unital_distill_copies}
\end{figure}
